The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-19 paper/sections/methods_ty.tex
backup Tys method section

\section{Methods}
Given a volumetric model composed of one or more NURBS surfaces, the surface of each surface is reconstructed using a set of control points $\textbf{p}$ and their associated weights $w$. Following D-NURBS \cite{10.1145/176579.176580}, we take our degrees of freedom (DOF) to be control points of the surfaces and produce displacements directly on these control points at each simulation step. We note that we used a simplified version of D-NURBS in which the weights are held constant throughout the simulation and find this not to be limiting \myworries{(feel like we'll need better justification than saying just this?)}. We represent the degrees of freedom for the $i$-th NURBS surface with $m$ control points as $\mathbf{q}_i = \left[ \mathbf{p}_1^T, \dots, \mathbf{p}_m^T \right]^T \in \mathbb{R}^{3m}$. From this definition, we write the DOF for the entire model as $\mathbf{q} = \left[ \mathbf{q}_i^T, \dots, \mathbf{q}_n^T \right]^T$ where $n$ is the number of NURBS surfaces for the model.

@@

In our algorithm, a single shape matching element is represented by a NURBS surface, a center of mass, and polynomial describing its current deformation. We construct these polynomials via a shape matching strategy. With the addition of the center of mass, we describe the shapes deformation about this point and thus the monomial basis in the case of a linear polynomial is $\left[ \mathbf 1^T (\mathbf{X - \bar{X}})^T \right]$ where $\mathbf 1^T$ is a constant $1$ column vector and $\mathbf{\bar{X}}$ is the center of mass for the element. To simplify the following formulas, we collect the non-constant terms of the monomial basis into a single vector $\mathbf{m}(\mathbf{X}-\mathbf{\bar{X}})$. For example if $\mathbf{X} = (X,Y,Z)$, $\mathbf{\bar{X}} = (\bar X, \bar Y, \bar Z)$, and $\mathbf{q}=\mathbf{X}-\mathbf{\bar{X}}$ with a quadratic polynomial we would have
\begin{equation}
m(\mathbf{q)} = (
					q_1, q_2, q_3,
                   	q_1^2, q_2^2, q_3^3,
                   	q_1 q_2, q_2 q_3
                ) \in \mathbb{R}^k
                \text{,}
\end{equation}
where $k$ is the size of the monomial basis. Next we arrange this basis into a matrix of the form
\begin{equation}
\mathbf{M}(\mathbf{q}) = \left[ \begin{array}{ccc}
\mathbf{m}(\mathbf{q}) &  &  \\
 & \mathbf{m}(\mathbf{q})  &  \\
 &  & \mathbf{m}(\mathbf{q})  \\
\end{array} \right] \in \mathbb{R}^{3x3k}
\text{.}
\end{equation}
With this definition of the monomial basis, we may reconstruct the deformed position $\mathbf{x}$ for some material point $\mathbf{X}$ with
\begin{equation}
\mathbf{x}(\mathbf{X}) = \left[\mathbf{M}(\mathbf{X-\bar{X}}) \quad \mathbf{I} \right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right]
\text{,}
\end{equation}
where $\mathbf{c} \in \mathbb{R}^{3k}$ is the set of polynomial coefficients for the non-constant terms, $\mathbf{t} \in \mathbb{R}^3$ is the constant term coefficients, and $\mathbf{I} \in \mathbb{R}^{3x3}$ is an identity matrix. The reason for separating out the constant term becomes more evident when we examine case where we have multiple elements.

@@

@@

>>>>

\section{Methods}
\dave{We should probably put some pseudo code for the preprocessing and the runtime algorithms right up fron, along with a quick textual walk through of the method.}
Given a volumetric model composed of one or more NURBS surfaces, the surface of each surface is reconstructed using a set of control points $\textbf{p}$ and their associated weights $w$. Following D-NURBS \cite{10.1145/176579.176580}, we take our degrees of freedom (DOF) to be control points of the surfaces and produce displacements directly on these control points at each simulation step. We note that we used a simplified version of D-NURBS in which the weights are held constant throughout the simulation and find this not to be limiting \myworries{(feel like we'll need better justification than saying just this?)}. We represent the degrees of freedom for the $i$-th NURBS surface with $m$ control points as $\mathbf{q}_i = \left[ \mathbf{p}_1^T, \dots, \mathbf{p}_m^T \right]^T \in \mathbb{R}^{3m}$. From this definition, we write the DOF for the entire model as $\mathbf{q} = \left[ \mathbf{q}_i^T, \dots, \mathbf{q}_n^T \right]^T$ where $n$ is the number of NURBS surfaces for the model.

@@

In our algorithm, a single shape matching element is represented by a NURBS surface, a center of mass, and polynomial describing its current deformation. We construct these polynomials via a shape matching strategy. With the addition of the center of mass, we describe the shapes deformation about this point and thus the monomial basis in the case of a linear polynomial is $\left[ \mathbf 1^T (\mathbf{X - \bar{X}})^T \right]$ where $\mathbf 1^T$ is a constant $1$ column vector and $\mathbf{\bar{X}}$ is the center of mass for the element. To simplify the following formulas, we collect the non-constant terms of the monomial basis into a single vector $\mathbf{m}(\mathbf{X}-\mathbf{\bar{X}})$. For example if $\mathbf{X} = (X,Y,Z)$, $\mathbf{\bar{X}} = (\bar X, \bar Y, \bar Z)$, and $\mathbf{q}=\mathbf{X}-\mathbf{\bar{X}}$ with a quadratic polynomial we would have

\begin{figure}
    \includegraphics[width=\columnwidth]{example-image-a}
    \caption{Figure showing shape matching to NURBS}
    \label{fig:shapematching}
\end{figure}

\begin{equation}
m(\mathbf{q)} = (
					q_1, q_2, q_3,
                   	q_1^2, q_2^2, q_3^3,
                   	q_1 q_2, q_2 q_3
                ) \in \mathbb{R}^k
                \text{,}
\end{equation}
where $k$ is the size of the monomial basis. Next we arrange this basis into a matrix of the form
\begin{equation}
\mathbf{M}(\mathbf{q}) = \left[ \begin{array}{ccc}
\mathbf{m}(\mathbf{q}) &  &  \\
 & \mathbf{m}(\mathbf{q})  &  \\
 &  & \mathbf{m}(\mathbf{q})  \\
\end{array} \right] \in \mathbb{R}^{3x3k}
\text{.}
\end{equation}
With this definition of the monomial basis, we may reconstruct the deformed position $\mathbf{x}$ for some material point $\mathbf{X}$ with
\begin{equation}
\mathbf{x}(\mathbf{X}) = \left[\mathbf{M}(\mathbf{X-\bar{X}}) \quad \mathbf{I} \right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right]
\text{,}
\end{equation}
where $\mathbf{c} \in \mathbb{R}^{3k}$ is the set of polynomial coefficients for the non-constant terms, $\mathbf{t} \in \mathbb{R}^3$ is the constant term coefficients, and $\mathbf{I} \in \mathbb{R}^{3x3}$ is an identity matrix. The reason for separating out the constant term becomes more evident when we examine case where we have multiple elements.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{example-image-a}
    \caption{Figure showing how weight calculation works (left) ray casting plus result (right) after correcting for partition of unity}
    \label{fig:weightcompute}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{example-image-a}
    \caption{Figure showing how raycasting quadrature works (top), convergence plot for volume integration (bottom}
    \label{fig:raycasting}
\end{figure}
